# Results

## Part I: Employees before and after COVID-19
```{r libs and df, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidyr)
library(readxl)
library(readr)
library(stringr)
library(ggplot2)
library(ggmosaic)
library(zoo)
library(RColorBrewer)

before <- read_csv("./data/before.csv")
after <- read_csv("./data/after.csv")
```

```{r,warning=F,message=F,echo=FALSE}
# using stacked bar plot to show the numbers of WFH people in each sector
before <- before[,-c(3,4)]
num_bef <- before%>%gather("Sector","Population",-c(Year,WFH_only))
wfh <- num_bef%>%filter(WFH_only==T)%>%select(Year,Sector,Population)
wfh$Year<- lubridate::ymd(wfh$Year, truncated = 2L)
ggplot(data = wfh,aes(x = Year,y = Population,fill = Sector))+
  geom_bar(stat = "identity")+
  scale_fill_brewer(palette="Set4")+
  ggtitle("Time Series Analysis on Telework Population for different Sectors")
```

Overall, the general population of telework employees tend to increase over the last 10 years. Among all the sectors being investigated, Service and Management,Business and Financial Sector seemed contribute to the increase in work-from-home employees' population the most.

```{r,warning=F,message=F,echo=FALSE}
#create line plots representing the change in WFH employees over total employed percentages before COVID
#calculate percentage table
totals <- seq(1,21,2)
wfh <- totals+1

before_perc <- before[wfh,]/before[totals,]
before_perc <- before_perc[,-ncol(before)]
before_perc$Year <- before$Year[totals]
#calculate percentage change
prev <- seq(1:10)
later <- prev+1
perc_change <- (before_perc[later,]-before_perc[prev,])/before_perc[prev,]
row.names(perc_change) <- before$Year[seq(3,22,2)]
perc_change <- perc_change[,-1]
new_perc_change <- gather(perc_change, columnNames, change)
colnames(new_perc_change)[1]<-"Sector"
Year <- rep(seq(2010,2019,1),8)
new_perc_change <- data.frame(new_perc_change,Year = lubridate::ymd(Year, truncated = 2L))

#construct plot
ggplot(new_perc_change,aes(x = Year,y = change))+
  geom_point(size=1, color="#69b3a2") +
  geom_line(color="#69b3a2")+
  geom_hline(yintercept=0,alpha = 0.3,color = "#69b3a2")+
  ggtitle('Time Series Analysis on the Growth Rate of \nWFH population in each sector before COVID \nper Year') +
  xlab("Year") +
  ylab("Growth Rate") + 
  geom_area(fill = "#69b3a2",alpha = 0.4)+
  facet_wrap(~Sector)+
  theme(plot.title = element_text(size = 20, face = "bold"))
```

The plot above shows the fluctuation of growth rate with WFH population within selected Sectors over years. We can see that some Sectors, such as Construction, Production, Office and Administration, Services and Transportation seem to have high volatility in the changes of WFH population percentages, with fluctuation ranging between -0.5% to 1%. Management, Business, Financial and Professional Sectors seem to have less fluctuation in the change of rate.


```{r,warning=F,message=F,echo=FALSE}
#change of WFH workers proportion over years
num_bef <- before%>%gather("Sector","Population",-c(Year,WFH_only))%>%group_by(Year,WFH_only)%>%summarise(Population = sum(Population))
totalemp_bef<-num_bef%>%filter(WFH_only==F)%>%select(Year,totalPop = Population)
wfh_bef<-num_bef%>%filter(WFH_only==T)%>%select(wfhPop = Population)
rate_bef <- data.frame(totalemp_bef$Year,perc = wfh_bef$wfhPop/totalemp_bef$totalPop)

num_aft <- after%>%gather("Sector","Population",-c(Year,WFH_only))%>%group_by(Year,WFH_only)%>%summarise(Population = sum(Population))
totalemp_aft<-num_aft%>%filter(WFH_only==F)%>%select(Time = Year,totalPop = Population)
wfh_aft<-num_aft%>%filter(WFH_only==T)%>%select(wfhPop = Population)
wfh_aft$Original <- totalemp_aft$totalPop-wfh_aft$wfhPop

wfh_aft<-wfh_aft%>%gather("Status","Population",-Year)

#stack bar plot for increase of wfh population due to covid
ggplot(data = wfh_aft,aes(x = Year,y = Population,fill = Status))+
  geom_bar(stat = "identity")+
  theme(axis.text.x=element_text(angle = 45)) +
  ggtitle("Time Series Analysis on \nthe Increase of Telework population due to COVID")

```

In general, we can see that the increase of telework population due to covid has a greater portion among the number of all employed workers starting from May 2020 and its proportion started to decrease as time pass by. Even though we could not get the data before May 2020, this trend may suggest that at the beginning of 2020, when COVID had just begun, the ratio of covid-lead WFH population over the total employed population would be even higher. Another trend we can see from the graph is that the total employed workers' number is gradually increasing.



## Part II: Productivity  
### Labor Productivity  
```{r,echo=FALSE}
library(dplyr)
# Import productivity data
business_pro <- read.csv("./data/business_productivity.csv", header=T,stringsAsFactors = F)
durable_goods_pro <- read.csv("./data/durable_goods_productivity.csv", header=T,stringsAsFactors = F)
non_durable_goods_pro <- read.csv("./data/non_durable_goods_productivity.csv", header=T,stringsAsFactors = F)
manufacturing_pro <- read.csv("./data/manufacturing_productivity.csv", header=T,stringsAsFactors = F)
nonfarm_business_pro <- read.csv("./data/nonfarm_business_productivity.csv", header=T,stringsAsFactors = F)
non_financial_corporations_pro <- read.csv("./data/non_financial_corporations_productivity.csv", header=T,stringsAsFactors = F)

```


```{r,echo=FALSE}
# Transform data and combine their rows into one productivity data frame
business_pro$Sector <- c("Business")
business_pro <- business_pro[,4:6]

nonfarm_business_pro$Sector <- c("Nonfarm Business")
nonfarm_business_pro <- nonfarm_business_pro[,4:6]

durable_goods_pro$Sector <- c("Durable Goods")
durable_goods_pro <- durable_goods_pro[,4:6]

non_durable_goods_pro$Sector <- c("Non Durable Goods")
non_durable_goods_pro <- non_durable_goods_pro[,4:6]

manufacturing_pro$Sector <- c("Manufacturing")
manufacturing_pro <- manufacturing_pro[,4:6]

non_financial_corporations_pro$Sector <- c("Non Financial Corporations")
non_financial_corporations_pro <- non_financial_corporations_pro[,4:6]

productivity <- rbind(business_pro,nonfarm_business_pro,durable_goods_pro,non_durable_goods_pro,manufacturing_pro,non_financial_corporations_pro)

```


```{r,echo=FALSE}
# Create Time series plot of productivity from 2018 to 2020
ggplot(data = productivity, aes(x = Label, y = Value,group = as.factor(Sector), color = Sector)) + 
  geom_line() + 
  theme(axis.text.x=element_text(angle = 45)) +
  ggtitle("Labor productivity from 2018 to 2020") +
  xlab("Time") + ylab("Output (per hour)")
ggplot(productivity,aes(x = Label, y = Value,group = as.factor(Sector)))+
  geom_point(size=1, color="#69b3a2") +
  geom_line(color="#69b3a2")+
  geom_hline(yintercept=0,alpha = 0.3,color = "#69b3a2")+
  ggtitle("Labor productivity from 2018 to 2020") +
  xlab("Time") +
  ylab("Output (per hour)") + 
  geom_area(fill = "#69b3a2",alpha = 0.4)+
  facet_wrap(~as.factor(Sector)) +
  theme(plot.title = element_text(size = 20, face = "bold"), axis.text.x=element_text(angle = 90))
```

From the time series plot and subplots, we can see that the output has a abrupt change at 2020 first and second quarter. Manufacturing and Durable Goods sectors have a sudden decrease and other sectors had a sudden increase. This might caused by the increasing number of Work From Home employees.  


 
### Work hours
```{r,echo=FALSE}
# Import weekly average work hours data
business_wh <- read.csv("./data/Index_business_avghours.csv", header=T,stringsAsFactors = F)
durable_goods_wh <- read.csv("./data/Index_durable_goods_avghours.csv", header=T,stringsAsFactors = F)
non_durable_goods_wh <- read.csv("./data/Index_non_durable_goods_avghours.csv", header=T,stringsAsFactors = F)
manufacturing_wh <- read.csv("./data/Index_manufacturing_avghours.csv", header=T,stringsAsFactors = F)
nonfarm_business_wh <- read.csv("./data/Index_nonfarm_business_avghours.csv", header=T,stringsAsFactors = F)
non_financial_corporations_wh <- read.csv("./data/Index_nonfinancial_avghours.csv", header=T,stringsAsFactors = F)
```



```{r,echo=FALSE}
# Transform data and combine their rows into one work_hours data frame
business_wh$Sector <- c("Business")
business_wh <- business_wh[,4:6]

nonfarm_business_wh$Sector <- c("Nonfarm Business")
nonfarm_business_wh <- nonfarm_business_wh[,4:6]

durable_goods_wh$Sector <- c("Durable Goods")
durable_goods_wh <- durable_goods_wh[,4:6]

non_durable_goods_wh$Sector <- c("Non Durable Goods")
non_durable_goods_wh <- non_durable_goods_wh[,4:6]

manufacturing_wh$Sector <- c("Manufacturing")
manufacturing_wh <- manufacturing_wh[,4:6]

non_financial_corporations_wh$Sector <- c("Non Financial Corporations")
non_financial_corporations_wh <- non_financial_corporations_wh[,4:6]

work_hours <- rbind(business_wh,nonfarm_business_wh,durable_goods_wh,non_durable_goods_wh,manufacturing_wh,non_financial_corporations_wh)
```



```{r,echo=FALSE}
# Create Time series plot of weekly average work hours from 2018 to 2020
ggplot(data = work_hours, aes(x = Label, y = Value,group = as.factor(Sector), color = Sector)) + 
  geom_line() + 
  theme(axis.text.x=element_text(angle = 45)) +
  ggtitle("Weekly Average Work Hours from 2018 to 2020") +
  xlab("Time") + ylab("Hours Worked")

```

Then we check work hours from 2018-2020. Work hours have apparent decrease for all sectors in the first quarter of 2020. This shows an opposite trend with productivity.  


### Unit labor cost
```{r,echo=FALSE}
# Import labor costs data
business_cost <- read.csv("./data/business_cost.csv", header=T,stringsAsFactors = F)
durable_goods_cost <- read.csv("./data/durable_goods_cost.csv", header=T,stringsAsFactors = F)
non_durable_goods_cost <- read.csv("./data/non_durable_goods_cost.csv", header=T,stringsAsFactors = F)
manufacturing_cost <- read.csv("./data/manufacturing_cost.csv", header=T,stringsAsFactors = F)
nonfarm_business_cost <- read.csv("./data/nonfarm_business_cost.csv", header=T,stringsAsFactors = F)
non_financial_corporations_cost <- read.csv("./data/nonfinancial_cost.csv", header=T,stringsAsFactors = F)
```



```{r,echo=FALSE}
# Transform data and combine their rows into one costs data frame
business_cost$Sector <- c("Business")
business_cost <- business_cost[,4:6]

nonfarm_business_cost$Sector <- c("Nonfarm Business")
nonfarm_business_cost <- nonfarm_business_cost[,4:6]

durable_goods_cost$Sector <- c("Durable Goods")
durable_goods_cost <- durable_goods_cost[,4:6]

non_durable_goods_cost$Sector <- c("Non Durable Goods")
non_durable_goods_cost <- non_durable_goods_cost[,4:6]

manufacturing_cost$Sector <- c("Manufacturing")
manufacturing_cost <- manufacturing_cost[,4:6]

non_financial_corporations_cost$Sector <- c("Non Financial Corporations")
non_financial_corporations_cost <- non_financial_corporations_cost[,4:6]

costs <- rbind(business_cost,nonfarm_business_cost,durable_goods_cost,non_durable_goods_cost,manufacturing_cost,non_financial_corporations_cost)
```



```{r,echo=FALSE}
# Create Time series plot of unit labor costs from 2018 to 2020
ggplot(data = costs, aes(x = Label, y = Value,group = as.factor(Sector), color = Sector)) + 
  geom_line() + 
  theme(axis.text.x=element_text(angle = 45)) +
  ggtitle("Labor Costs from 2018 to 2020") +
  xlab("Time") + ylab("Unit Labor Cost")

```

We check unit labor cost from 2018-2020 and find the costs increase a lot in 2020 first quarter. Since three time series plots all show that there is a sudden change at 2020 first quarter, the pandemic could be the cause.  


### Relationship between Producitivity and Work From Home employees
```{r,echo=FALSE}
WFH_business <- read.csv("./data/WFH_business.csv", header=T,stringsAsFactors = F)
WFH_manufacturing <- read.csv("./data/WFH_manufacturing.csv", header=T,stringsAsFactors = F)
WFH_durable_goods <- read.csv("./data/WFH_durable_goods.csv", header=T,stringsAsFactors = F)
WFH_non_durable_goods <- read.csv("./data/WFH_non_durable_goods.csv", header=T,stringsAsFactors = F)
WFH_non_financial <- read.csv("./data/WFH_non_financial.csv", header=T,stringsAsFactors = F)
WFH_nonfarm <- read.csv("./data/WFH_nonfarm_business.csv", header=T,stringsAsFactors = F)

```


```{r,echo=FALSE}
# Calculate work from home percentage by month.
WFH_business$WFM_pct <- WFH_business$WFM/WFH_business$Total
WFH_manufacturing$WFM_pct <- WFH_manufacturing$WFM/WFH_manufacturing$Total
WFH_durable_goods$WFM_pct <- WFH_durable_goods$WFM/WFH_durable_goods$Total
WFH_non_durable_goods$WFM_pct <- WFH_non_durable_goods$WFM/WFH_non_durable_goods$Total
WFH_non_financial$WFM_pct <- WFH_non_financial$WFM/WFH_non_financial$Total
WFH_nonfarm$WFM_pct <- WFH_nonfarm$WFM/WFH_nonfarm$Total
WFH_employee <- rbind(WFH_business,WFH_durable_goods,WFH_manufacturing,WFH_non_durable_goods,WFH_non_financial,WFH_nonfarm)
WFH_employee$Time <- as.Date(paste(WFH_employee$Time,"01"),"%Y %b %d")
WFH_employee$Time <- substr(WFH_employee$Time,6,7)
```



```{r,echo=FALSE}
# Time series plot of WFH employees percentage by month
ggplot(data = WFH_employee, aes(x = Time, y = WFM_pct,group = as.factor(Sector), color = Sector)) + 
  geom_line() + 
  ggtitle("WFH employees in 2020") +
  xlab("Month") + ylab("Percent of WFH Employees")
```

The graph represents the percentage of Work From Home Employees change due to the pandemic. There is a decreasing trend from May to October and lines slightly back up in November and December.  


```{r,echo=FALSE}
# Compute　data to quarterly based for WFH employees
WFH_2020 <- WFH_employee %>% group_by(Sector,Label) %>%
  summarize(mean_WFM = mean(WFM, na.rm = TRUE),mean_total = mean(Total, na.rm = TRUE), .groups = 'drop')
WFH_2020 <- WFH_2020[-15, ]
WFH_2020$WFM_qt_pct <- WFH_2020$mean_WFM/WFH_2020$mean_total
WFH_2020 <- WFH_2020[,c("Sector","Label","WFM_qt_pct")]
# Select 2020 data from producitivity
qts <- WFH_business$Label
prod_2020 <- productivity %>% filter(Label=="2020 Qtr2" | Label=="2020 Qtr3" | Label=="2020 Qtr4")
prod_2020 <- prod_2020[order(prod_2020$Sector, prod_2020$Label),]
# Column bind two dfs together
WFH_prod_df <- cbind(WFH_2020,prod_2020)
WFH_prod_df <- WFH_prod_df[,c("Sector","Label","WFM_qt_pct","Value")]
```


```{r,echo=FALSE}
# Check scatterplot for the relationship between productivity and WFH employees 
ggplot(data = WFH_prod_df, aes(x = WFM_qt_pct, y = Value)) + 
  geom_point()+
  geom_smooth(method=lm, se=FALSE) + 
  ggtitle("Scatterplot of Productivity and WFH employees") +
  xlab("Percent of WFH Employees") + ylab("Productivity")

```

From the previous sections, we find that Work hours decrease and production increase in first and sector quarter of 2020. This means that the efficiency has increased, which might be caused by teleworking. Hence, we make a scatter plot to illustrate the relationship between Productivity and WFH employees. The scatterplot indicates that there is a positive correlation between two variables. As the percentage of WFH employees increase, the Productivity tends to increase.  


## Part III: Employment and earnings

```{r}
data_processing <- function(path) {
  df_raw <- read_excel(path, range = "A13:M24")
  df <- data.frame(matrix(ncol = 4, nrow = 0))
  colnames(df) <- c('Year', 'Month', 'Label', 'Value')
  k=1
  for (i in 1:11){
    for (j in 2:13){
      df[k, 'Value'] = df_raw[i,j]
      df[k, 'Year'] = df_raw[i,1]
      df[k, 'Month'] = names(df_raw)[j]
      df[k, 'Lable'] = paste(df_raw[i,1],  names(df_raw)[j])
      k <- k+1
    }
  }
  df <- df[1:123,]
  return(df)
}
```

### Employee numbers

```{r, echo=FALSE}
# Import and transform employees data

EmployeesTotalPrivate <- data_processing("data/EmployeesTotalPrivate.xlsx")
EmployeesGoodsProducing <- data_processing("data/EmployeesGoodsProducing.xlsx")
EmployeesGPMiningLogging <- data_processing("data/EmployeesGPMiningLogging.xlsx")
EmployeesGPConstruction <- data_processing("data/EmployeesGPConstruction.xlsx")
EmployeesGPManufacturing <- data_processing("data/EmployeesGPManufacturing.xlsx")
EmployeesGPMDurableGoods <- data_processing("data/EmployeesGPMDurableGoods.xlsx")
EmployeesGPMNondurableGoods <- data_processing("data/EmployeesGPMNondurableGoods.xlsx")
EmployeesServiceProviding <- data_processing("data/EmployeesServiceProviding.xlsx")
EmployeesSPEducationHealthServices <- data_processing("data/EmployeesSPEducationHealthServices.xlsx")
EmployeesSPFinancialActivities <- data_processing("data/EmployeesSPFinancialActivities.xlsx")
EmployeesSPInformation <- data_processing("data/EmployeesSPInformation.xlsx")
EmployeesSPLeisureHospitality <- data_processing("data/EmployeesSPLeisureHospitality.xlsx")
EmployeesSPOtherServices <- data_processing("data/EmployeesSPOtherServices.xlsx")
EmployeesSPProfessionalBusinessService <- data_processing("data/EmployeesSPProfessionalBusinessService.xlsx")
EmployeesSPTradeTransportationUtilities <- data_processing("data/EmployeesSPTradeTransportationUtilities.xlsx")
EmployeesSPTTURetail <- data_processing("data/EmployeesSPTTURetail.xlsx")
EmployeesSPTTUTransportationWarehousing <- data_processing("data/EmployeesSPTTUTransportationWarehousing.xlsx")
EmployeesSPTTUUtilities <- data_processing("data/EmployeesSPTTUUtilities.xlsx")
EmployeesSPTTUWholesale <- data_processing("data/EmployeesSPTTUWholesale.xlsx")
```

```{r, echo=FALSE}
# assign sectors

EmployeesTotalPrivate$Sector <- c("Total Private")
EmployeesTotalPrivate$SubSector <- c("Total Private")
EmployeesTotalPrivate$Industry <- c("Total Private")
EmployeesGoodsProducing$Sector <- c("Goods-producing")
EmployeesGoodsProducing$SubSector <- c("Goods-producing")
EmployeesGoodsProducing$Industry <- c("Goods-producing")
EmployeesGPMiningLogging$Sector <- c("Goods-producing")
EmployeesGPMiningLogging$SubSector <- c("Mining and Logging")
EmployeesGPMiningLogging$Industry <- c("Mining and Logging")
EmployeesGPConstruction$Sector <- c("Goods-producing")
EmployeesGPConstruction$SubSector <- c("Construction")
EmployeesGPConstruction$Industry <- c("Construction")
EmployeesGPManufacturing$Sector <- c("Goods-producing")
EmployeesGPManufacturing$SubSector <- c("Manufacturing")
EmployeesGPManufacturing$Industry <- c("Manufacturing")
EmployeesGPMDurableGoods$Sector <- c("Goods-producing")
EmployeesGPMDurableGoods$SubSector <- c("Manufacturing")
EmployeesGPMDurableGoods$Industry <- c("Durable Goods")
EmployeesGPMNondurableGoods$Sector <- c("Goods-producing")
EmployeesGPMNondurableGoods$SubSector <- c("Manufacturing")
EmployeesGPMNondurableGoods$Industry <- c("Nondurable Goods")
EmployeesServiceProviding$Sector <- c("Private Service Providing")
EmployeesServiceProviding$SubSector <- c("Private Service Providing")
EmployeesServiceProviding$Industry <- c("Private Service Providing")
EmployeesSPEducationHealthServices$Sector <- c("Private Service Providing")
EmployeesSPEducationHealthServices$SubSector <- c("Education and Health Services")
EmployeesSPEducationHealthServices$Industry <- c("Education and Health Services")
EmployeesSPFinancialActivities$Sector <- c("Private Service Providing")
EmployeesSPFinancialActivities$SubSector <- c("Financial Activities")
EmployeesSPFinancialActivities$Industry <- c("Financial Activities")
EmployeesSPInformation$Sector <- c("Private Service Providing")
EmployeesSPInformation$SubSector <- c("Information")
EmployeesSPInformation$Industry <- c("Information")
EmployeesSPLeisureHospitality$Sector <- c("Private Service Providing")
EmployeesSPLeisureHospitality$SubSector <- c("Leisure and Hospitality")
EmployeesSPLeisureHospitality$Industry <- c("Leisure and Hospitality")
EmployeesSPOtherServices$Sector <- c("Private Service Providing")
EmployeesSPOtherServices$SubSector <- c("Other Services")
EmployeesSPOtherServices$Industry <- c("Other Services")
EmployeesSPProfessionalBusinessService$Sector <- c("Private Service Providing")
EmployeesSPProfessionalBusinessService$SubSector <- c("Professional and Business Service")
EmployeesSPProfessionalBusinessService$Industry <- c("Professional and Business Service")
EmployeesSPTradeTransportationUtilities$Sector <- c("Private Service Providing")
EmployeesSPTradeTransportationUtilities$SubSector <- c("Trade Transportation and Utilities")
EmployeesSPTradeTransportationUtilities$Industry <- c("Trade Transportation and Utilities")
EmployeesSPTTURetail$Sector <- c("Private Service Providing")
EmployeesSPTTURetail$SubSector <- c("Trade Transportation and Utilities")
EmployeesSPTTURetail$Industry <- c("Retail Trade")
EmployeesSPTTUTransportationWarehousing$Sector <- c("Private Service Providing")
EmployeesSPTTUTransportationWarehousing$SubSector <- c("Trade Transportation and Utilities")
EmployeesSPTTUTransportationWarehousing$Industry <- c("Transportation and Warehousing")
EmployeesSPTTUUtilities$Sector <- c("Private Service Providing")
EmployeesSPTTUUtilities$SubSector <- c("Trade Transportation and Utilities")
EmployeesSPTTUUtilities$Industry <- c("Utilities")
EmployeesSPTTUWholesale$Sector <- c("Private Service Providing")
EmployeesSPTTUWholesale$SubSector <- c("Trade Transportation and Utilities")
EmployeesSPTTUWholesale$Industry <- c("Wholesale Trade")
```

```{r, echo=FALSE}
# combine tables
employees_num <- rbind(EmployeesTotalPrivate, EmployeesGoodsProducing, EmployeesGPMiningLogging, EmployeesGPConstruction, EmployeesGPManufacturing, EmployeesGPMDurableGoods, EmployeesGPMNondurableGoods, EmployeesServiceProviding, EmployeesSPEducationHealthServices, EmployeesSPFinancialActivities, EmployeesSPInformation, EmployeesSPLeisureHospitality, EmployeesSPOtherServices, EmployeesSPProfessionalBusinessService, EmployeesSPTradeTransportationUtilities, EmployeesSPTTURetail, EmployeesSPTTUTransportationWarehousing, EmployeesSPTTUUtilities, EmployeesSPTTUWholesale)
```

### Average weekly working hours and overtime hours
#### weekly working hours
```{r, echo=FALSE}
# Import and transform working hour data

WklyHrTotalPrivate <- data_processing("data/WklyHrTotalPrivate.xlsx")
WklyHrGoodsProducing <- data_processing("data/WklyHrGoodsProducing.xlsx")
WklyHrGPMiningLogging <- data_processing("data/WklyHrGPMiningLogging.xlsx")
WklyHrGPConstruction <- data_processing("data/WklyHrGPConstruction.xlsx")
WklyHrGPManufacturing <- data_processing("data/WklyHrGPManufacturing.xlsx")
WklyHrGPMDurableGoods <- data_processing("data/WklyHrGPMDurableGoods.xlsx")
WklyHrGPMNondurableGoods <- data_processing("data/WklyHrGPMNondurableGoods.xlsx")
WklyHrServiceProviding <- data_processing("data/WklyHrServiceProviding.xlsx")
WklyHrSPEducationHealthServices <- data_processing("data/WklyHrSPEducationHealthServices.xlsx")
WklyHrSPFinancialActivities <- data_processing("data/WklyHrSPFinancialActivities.xlsx")
WklyHrSPInformation <- data_processing("data/WklyHrSPInformation.xlsx")
WklyHrSPLeisureHospitality <- data_processing("data/WklyHrSPLeisureHospitality.xlsx")
WklyHrSPOtherServices <- data_processing("data/WklyHrSPOtherServices.xlsx")
WklyHrSPProfessionalBusinessService <- data_processing("data/WklyHrSPProfessionalBusinessServices.xlsx")
WklyHrSPTradeTransportationUtilities <- data_processing("data/WklyHrSPTradeTransportationUtilities.xlsx")
WklyHrSPTTURetail <- data_processing("data/WklyHrSPTTURetail.xlsx")
WklyHrSPTTUTransportationWarehousing <- data_processing("data/WklyHrSPTTUTransportationWarehousing.xlsx")
WklyHrSPTTUUtilities <- data_processing("data/WklyHrSPTTUUtilities.xlsx")
WklyHrSPTTUWholesale <- data_processing("data/WklyHrSPTTUWholesale.xlsx")
```

```{r, echo=FALSE}
# assign sectors

WklyHrTotalPrivate$Sector <- c("Total Private")
WklyHrTotalPrivate$SubSector <- c("Total Private")
WklyHrTotalPrivate$Industry <- c("Total Private")
WklyHrGoodsProducing$Sector <- c("Goods-producing")
WklyHrGoodsProducing$SubSector <- c("Goods-producing")
WklyHrGoodsProducing$Industry <- c("Goods-producing")
WklyHrGPMiningLogging$Sector <- c("Goods-producing")
WklyHrGPMiningLogging$SubSector <- c("Mining and Logging")
WklyHrGPMiningLogging$Industry <- c("Mining and Logging")
WklyHrGPConstruction$Sector <- c("Goods-producing")
WklyHrGPConstruction$SubSector <- c("Construction")
WklyHrGPConstruction$Industry <- c("Construction")
WklyHrGPManufacturing$Sector <- c("Goods-producing")
WklyHrGPManufacturing$SubSector <- c("Manufacturing")
WklyHrGPManufacturing$Industry <- c("Manufacturing")
WklyHrGPMDurableGoods$Sector <- c("Goods-producing")
WklyHrGPMDurableGoods$SubSector <- c("Manufacturing")
WklyHrGPMDurableGoods$Industry <- c("Durable Goods")
WklyHrGPMNondurableGoods$Sector <- c("Goods-producing")
WklyHrGPMNondurableGoods$SubSector <- c("Manufacturing")
WklyHrGPMNondurableGoods$Industry <- c("Nondurable Goods")
WklyHrServiceProviding$Sector <- c("Private Service Providing")
WklyHrServiceProviding$SubSector <- c("Private Service Providing")
WklyHrServiceProviding$Industry <- c("Private Service Providing")
WklyHrSPEducationHealthServices$Sector <- c("Private Service Providing")
WklyHrSPEducationHealthServices$SubSector <- c("Education and Health Services")
WklyHrSPEducationHealthServices$Industry <- c("Education and Health Services")
WklyHrSPFinancialActivities$Sector <- c("Private Service Providing")
WklyHrSPFinancialActivities$SubSector <- c("Financial Activities")
WklyHrSPFinancialActivities$Industry <- c("Financial Activities")
WklyHrSPInformation$Sector <- c("Private Service Providing")
WklyHrSPInformation$SubSector <- c("Information")
WklyHrSPInformation$Industry <- c("Information")
WklyHrSPLeisureHospitality$Sector <- c("Private Service Providing")
WklyHrSPLeisureHospitality$SubSector <- c("Leisure and Hospitality")
WklyHrSPLeisureHospitality$Industry <- c("Leisure and Hospitality")
WklyHrSPOtherServices$Sector <- c("Private Service Providing")
WklyHrSPOtherServices$SubSector <- c("Other Services")
WklyHrSPOtherServices$Industry <- c("Other Services")
WklyHrSPProfessionalBusinessService$Sector <- c("Private Service Providing")
WklyHrSPProfessionalBusinessService$SubSector <- c("Professional and Business Service")
WklyHrSPProfessionalBusinessService$Industry <- c("Professional and Business Service")
WklyHrSPTradeTransportationUtilities$Sector <- c("Private Service Providing")
WklyHrSPTradeTransportationUtilities$SubSector <- c("Trade Transportation and Utilities")
WklyHrSPTradeTransportationUtilities$Industry <- c("Trade Transportation and Utilities")
WklyHrSPTTURetail$Sector <- c("Private Service Providing")
WklyHrSPTTURetail$SubSector <- c("Trade Transportation and Utilities")
WklyHrSPTTURetail$Industry <- c("Retail Trade")
WklyHrSPTTUTransportationWarehousing$Sector <- c("Private Service Providing")
WklyHrSPTTUTransportationWarehousing$SubSector <- c("Trade Transportation and Utilities")
WklyHrSPTTUTransportationWarehousing$Industry <- c("Transportation and Warehousing")
WklyHrSPTTUUtilities$Sector <- c("Private Service Providing")
WklyHrSPTTUUtilities$SubSector <- c("Trade Transportation and Utilities")
WklyHrSPTTUUtilities$Industry <- c("Utilities")
WklyHrSPTTUWholesale$Sector <- c("Private Service Providing")
WklyHrSPTTUWholesale$SubSector <- c("Trade Transportation and Utilities")
WklyHrSPTTUWholesale$Industry <- c("Wholesale Trade")
```

```{r, echo=FALSE}
# combine tables
WklyHr <- rbind(WklyHrTotalPrivate, WklyHrGoodsProducing, WklyHrGPMiningLogging, WklyHrGPConstruction, WklyHrGPManufacturing, WklyHrGPMDurableGoods, WklyHrGPMNondurableGoods, WklyHrServiceProviding, WklyHrSPEducationHealthServices, WklyHrSPFinancialActivities, WklyHrSPInformation, WklyHrSPLeisureHospitality, WklyHrSPOtherServices, WklyHrSPProfessionalBusinessService, WklyHrSPTradeTransportationUtilities, WklyHrSPTTURetail, WklyHrSPTTUTransportationWarehousing, WklyHrSPTTUUtilities, WklyHrSPTTUWholesale)
```

#### Weekly overtime hours

```{r, echo=FALSE}
# Import and transform overtime data

WklyOvertimeGPManufacturing <- data_processing("data/WklyOvertimeManufacturing.xlsx")
WklyOvertimeGPMDurableGoods <- data_processing("data/WklyOvertimeMDurableGoods.xlsx")
WklyOvertimeGPMNondurableGoods <- data_processing("data/WklyOvertimeMNondurableGoods.xlsx")

# assign sectors

WklyOvertimeGPManufacturing$Sector <- c("Goods-producing")
WklyOvertimeGPManufacturing$SubSector <- c("Manufacturing")
WklyOvertimeGPManufacturing$Industry <- c("Manufacturing")
WklyOvertimeGPMDurableGoods$Sector <- c("Goods-producing")
WklyOvertimeGPMDurableGoods$SubSector <- c("Manufacturing")
WklyOvertimeGPMDurableGoods$Industry <- c("Durable Goods")
WklyOvertimeGPMNondurableGoods$Sector <- c("Goods-producing")
WklyOvertimeGPMNondurableGoods$SubSector <- c("Manufacturing")
WklyOvertimeGPMNondurableGoods$Industry <- c("Nondurable Goods")

# combine tables
WklyOvertime <- rbind(WklyOvertimeGPManufacturing, WklyOvertimeGPMDurableGoods, WklyOvertimeGPMNondurableGoods)
```

### Average hourly earnings

```{r, echo=FALSE}
# Import and transform hourly earnings data

HrlyEarningsTotalPrivate <- data_processing("data/HrlyEarningsTotalPrivate.xlsx")
HrlyEarningsGoodsProducing <- data_processing("data/HrlyEarningsGoodsProducing.xlsx")
HrlyEarningsGPMiningLogging <- data_processing("data/HrlyEarningsGPMiningLogging.xlsx")
HrlyEarningsGPConstruction <- data_processing("data/HrlyEarningsGPConstruction.xlsx")
HrlyEarningsGPManufacturing <- data_processing("data/HrlyEarningsGPManufacturing.xlsx")
HrlyEarningsGPMDurableGoods <- data_processing("data/HrlyEarningsGPMDurableGoods.xlsx")
HrlyEarningsGPMNondurableGoods <- data_processing("data/HrlyEarningsGPMNondurableGoods.xlsx")
HrlyEarningsServiceProviding <- data_processing("data/HrlyEarningsServiceProviding.xlsx")
HrlyEarningsSPEducationHealthServices <- data_processing("data/HrlyEarningsSPEducationHealthServices.xlsx")
HrlyEarningsSPFinancialActivities <- data_processing("data/HrlyEarningsSPFinancialActivities.xlsx")
HrlyEarningsSPInformation <- data_processing("data/HrlyEarningsSPInformation.xlsx")
HrlyEarningsSPLeisureHospitality <- data_processing("data/HrlyEarningsSPLeisureHospitality.xlsx")
HrlyEarningsSPOtherServices <- data_processing("data/HrlyEarningsSPOtherServices.xlsx")
HrlyEarningsSPProfessionalBusinessService <- data_processing("data/HrlyEarningsSPProfessionalBusinessServices.xlsx")
HrlyEarningsSPTradeTransportationUtilities <- data_processing("data/HrlyEarningsSPTradeTransportationUtilities.xlsx")
HrlyEarningsSPTTURetail <- data_processing("data/HrlyEarningsSPTTURetail.xlsx")
HrlyEarningsSPTTUTransportationWarehousing <- data_processing("data/HrlyEarningsSPTTUTransportationWarehousing.xlsx")
HrlyEarningsSPTTUUtilities <- data_processing("data/HrlyEarningsSPTTUUtilities.xlsx")
HrlyEarningsSPTTUWholesale <- data_processing("data/HrlyEarningsSPTTUWholesale.xlsx")
```

```{r, echo=FALSE}
# assign sectors

HrlyEarningsTotalPrivate$Sector <- c("Total Private")
HrlyEarningsTotalPrivate$SubSector <- c("Total Private")
HrlyEarningsTotalPrivate$Industry <- c("Total Private")
HrlyEarningsGoodsProducing$Sector <- c("Goods-producing")
HrlyEarningsGoodsProducing$SubSector <- c("Goods-producing")
HrlyEarningsGoodsProducing$Industry <- c("Goods-producing")
HrlyEarningsGPMiningLogging$Sector <- c("Goods-producing")
HrlyEarningsGPMiningLogging$SubSector <- c("Mining and Logging")
HrlyEarningsGPMiningLogging$Industry <- c("Mining and Logging")
HrlyEarningsGPConstruction$Sector <- c("Goods-producing")
HrlyEarningsGPConstruction$SubSector <- c("Construction")
HrlyEarningsGPConstruction$Industry <- c("Construction")
HrlyEarningsGPManufacturing$Sector <- c("Goods-producing")
HrlyEarningsGPManufacturing$SubSector <- c("Manufacturing")
HrlyEarningsGPManufacturing$Industry <- c("Manufacturing")
HrlyEarningsGPMDurableGoods$Sector <- c("Goods-producing")
HrlyEarningsGPMDurableGoods$SubSector <- c("Manufacturing")
HrlyEarningsGPMDurableGoods$Industry <- c("Durable Goods")
HrlyEarningsGPMNondurableGoods$Sector <- c("Goods-producing")
HrlyEarningsGPMNondurableGoods$SubSector <- c("Manufacturing")
HrlyEarningsGPMNondurableGoods$Industry <- c("Nondurable Goods")
HrlyEarningsServiceProviding$Sector <- c("Private Service Providing")
HrlyEarningsServiceProviding$SubSector <- c("Private Service Providing")
HrlyEarningsServiceProviding$Industry <- c("Private Service Providing")
HrlyEarningsSPEducationHealthServices$Sector <- c("Private Service Providing")
HrlyEarningsSPEducationHealthServices$SubSector <- c("Education and Health Services")
HrlyEarningsSPEducationHealthServices$Industry <- c("Education and Health Services")
HrlyEarningsSPFinancialActivities$Sector <- c("Private Service Providing")
HrlyEarningsSPFinancialActivities$SubSector <- c("Financial Activities")
HrlyEarningsSPFinancialActivities$Industry <- c("Financial Activities")
HrlyEarningsSPInformation$Sector <- c("Private Service Providing")
HrlyEarningsSPInformation$SubSector <- c("Information")
HrlyEarningsSPInformation$Industry <- c("Information")
HrlyEarningsSPLeisureHospitality$Sector <- c("Private Service Providing")
HrlyEarningsSPLeisureHospitality$SubSector <- c("Leisure and Hospitality")
HrlyEarningsSPLeisureHospitality$Industry <- c("Leisure and Hospitality")
HrlyEarningsSPOtherServices$Sector <- c("Private Service Providing")
HrlyEarningsSPOtherServices$SubSector <- c("Other Services")
HrlyEarningsSPOtherServices$Industry <- c("Other Services")
HrlyEarningsSPProfessionalBusinessService$Sector <- c("Private Service Providing")
HrlyEarningsSPProfessionalBusinessService$SubSector <- c("Professional and Business Service")
HrlyEarningsSPProfessionalBusinessService$Industry <- c("Professional and Business Service")
HrlyEarningsSPTradeTransportationUtilities$Sector <- c("Private Service Providing")
HrlyEarningsSPTradeTransportationUtilities$SubSector <- c("Trade Transportation and Utilities")
HrlyEarningsSPTradeTransportationUtilities$Industry <- c("Trade Transportation and Utilities")
HrlyEarningsSPTTURetail$Sector <- c("Private Service Providing")
HrlyEarningsSPTTURetail$SubSector <- c("Trade Transportation and Utilities")
HrlyEarningsSPTTURetail$Industry <- c("Retail Trade")
HrlyEarningsSPTTUTransportationWarehousing$Sector <- c("Private Service Providing")
HrlyEarningsSPTTUTransportationWarehousing$SubSector <- c("Trade Transportation and Utilities")
HrlyEarningsSPTTUTransportationWarehousing$Industry <- c("Transportation and Warehousing")
HrlyEarningsSPTTUUtilities$Sector <- c("Private Service Providing")
HrlyEarningsSPTTUUtilities$SubSector <- c("Trade Transportation and Utilities")
HrlyEarningsSPTTUUtilities$Industry <- c("Utilities")
HrlyEarningsSPTTUWholesale$Sector <- c("Private Service Providing")
HrlyEarningsSPTTUWholesale$SubSector <- c("Trade Transportation and Utilities")
HrlyEarningsSPTTUWholesale$Industry <- c("Wholesale Trade")
```

```{r, echo=FALSE}
# combine tables
HrlyEarnings <- rbind(HrlyEarningsTotalPrivate, HrlyEarningsGoodsProducing, HrlyEarningsGPMiningLogging, HrlyEarningsGPConstruction, HrlyEarningsGPManufacturing, HrlyEarningsGPMDurableGoods, HrlyEarningsGPMNondurableGoods, HrlyEarningsServiceProviding, HrlyEarningsSPEducationHealthServices, HrlyEarningsSPFinancialActivities, HrlyEarningsSPInformation, HrlyEarningsSPLeisureHospitality, HrlyEarningsSPOtherServices, HrlyEarningsSPProfessionalBusinessService, HrlyEarningsSPTradeTransportationUtilities, HrlyEarningsSPTTURetail, HrlyEarningsSPTTUTransportationWarehousing, HrlyEarningsSPTTUUtilities, HrlyEarningsSPTTUWholesale)
```
